Do NBA Teams Avoid Trading within Their Own Division?

### 2023-08-07 Manuscript.qmd
Fix competing interests
format keywords properly

---
title: "Do NBA Teams Avoid Trading within Their Own Division?"
author: 
  - name: jimi adams
    orcid: "0000-0001-5043-1149"
    email: "JIMI.ADAMS@ucdenver.edu"
    affiliations: 
      - name: "University of Colorado Denver"
        city: "Denver, CO"
        country: USA
        postal-code: "80217-3364"
  - name: Michał Bojanowski
    orcid: "0000-0001-7503-852X"
    affiliations:
      - name: "Autonomous University of Barcelona"
        city: "Bellaterra (Barcelona)"
        country: Spain
        postal-code: "08-193"
      - name: "Kozminski University"
        city: Warsaw
        country: Poland
        postal-code: "03-301"
date: "May 10, 2022"
abstract: "Within US professional sports, trades within one's own division are often perceived to be disadvantageous. We ask how common this practice is. To examine this question, we construct a date-stamped network of all trades in the NBA between June 1976 and May 2019. We then use season-specific weighted exponential random graph models to estimate the likelihood of teams avoiding within-division trade partners, and how consistent that pattern is across the observed period. In addition to the empirical question, this analysis serves to demonstrate the necessity and difficulty of constructing the proper baseline for statistical comparison. We find limited-to-no support for the popular perception."
keywords: [trade networks, nba, sports, exponential random graph models, weighted networks]
format: 
  cambridge-medium-pdf:
    keep-tex: true
    cite-method: biblatex
    number-sections: true
    journal: nws
    year: 2023
    volume: NA
repository_url: https://github.com/mbojan/nba-trades
bibliography: nba-trades.bib
editor_options: 
  chunk_output_type: console
---

@@

\paragraph{Competing interests} None.

>>>>

---
title: "Do NBA Teams Avoid Trading within Their Own Division?"
author: 
  - name: jimi adams
    orcid: "0000-0001-5043-1149"
    email: "JIMI.ADAMS@ucdenver.edu"
    affiliations: 
      - name: "University of Colorado Denver"
        city: "Denver, CO"
        country: USA
        postal-code: "80217-3364"
  - name: Michał Bojanowski
    orcid: "0000-0001-7503-852X"
    affiliations:
      - name: "Autonomous University of Barcelona"
        city: "Bellaterra (Barcelona)"
        country: Spain
        postal-code: "08-193"
      - name: "Kozminski University"
        city: Warsaw
        country: Poland
        postal-code: "03-301"
date: "May 10, 2022"
abstract: "Within US professional sports, trades within one's own division are often perceived to be disadvantageous. We ask how common this practice is. To examine this question, we construct a date-stamped network of all trades in the NBA between June 1976 and May 2019. We then use season-specific weighted exponential random graph models to estimate the likelihood of teams avoiding within-division trade partners, and how consistent that pattern is across the observed period. In addition to the empirical question, this analysis serves to demonstrate the necessity and difficulty of constructing the proper baseline for statistical comparison. We find limited-to-no support for the popular perception."
keywords: ["trade networks", "NBA", "sports", "Exponential-family Random Graph Models", "weighted networks"]
format: 
  cambridge-medium-pdf:
    keep-tex: true
    cite-method: biblatex
    number-sections: true
    journal: nws
    year: 2023
    volume: NA
repository_url: https://github.com/mbojan/nba-trades
bibliography: nba-trades.bib
editor_options: 
  chunk_output_type: console
---

@@

Competing interests. None.
